---
title: "kermit perceptions rank based tests"
author: "Michael Allen"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Michael says hello
Kirby says hi

if you are the collaborator:
- load tidyverse
-read in the kermit data as 'kermit'
- make some side-by-side histograms of the score.pre for all respondents, seperated by the gender column 

```{r}
#load relevant libraries and data

library(tidyverse)
kermit <- read_csv("kermit.csv")

hist_kermit <- 
  ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender) + 
  theme_classic()

hist_kermit
```

Is there a significant difference in pre-talk ranks of kermit for male and female respondents

```{r}
mwu_kermit <- kermit %>%
  wilcox.test(Score.pre ~ Gender, data = .)

# H0: there is not a significant difference in ranks of male and female respondents
# H1: there is...

mwu_kermit

```

There was no significant difference in ranks for male and female respondents (W = 155.5, p = 0.4, alpha = 0.05).